\Title

### 2022-09-29 Grimaldi-etal-BiolCybernetics.tex
introduction

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
Machine learning, and computer vision in particular, have undergone a major transformation in modern times, leaving science fiction movies to become mainstream tools found in the smartphones in everyone's pocket. Less visible, but even more crucial to our economy and security, are the many automated tools that now dominate the range of services that equip virtually all sectors of our daily lives. This trend is most pronounced in the field of medicine, as it provides practitioners with new diagnostic tools to treat people faster and more effectively. This particular example also illustrates some important challenges that these tools are increasingly facing. One of these is their sensitivity to adversarial attacks, that is, the sensitivity of the models' output to minute changes in the input. This could raise important questions about the reliability of the results of in any automated diagnostic model. More generally, these models do not explain why they produce a given output for a class of inputs. This lack of explainability is a hindrance to the advancement of these methodologies as well as to their acceptance for most safety-relevant tasks. If we take a step back, we will remember that these tools are inherited from theoretical models designed to understand the brain. While the first artificial neural networks were mainly applied to toy-like problems, they also offered a growing number of applications in computer vision, but also more generally for task automation. In particular, convolutional neural networks are inspired by the feed-forward processing observed in the visual pathways of primates, and today they reach higher performances than humans for image categorization. One of the challenges of these models is to be able to scale them up for future applications, for example in autonomous driving. Indeed, in such applications, the input does not consist of a single image (say a few million pixels) but of a continuous stream of images from several cameras.

The challenges are numerous in such situations and two major obstacles must be highlighted: the computational delay and the energy budget. First, most existing solutions are built incrementally from models built to process low definition images, such as Le Net for MNIST~\citep{lecun1998gradient}, to high definition images, such as VGG on Imagenet~\citep{Simonyan:2014cmh}. This has a cost and notably the fact that the computation time increases with the size of the image. This phenomenon has been mitigated by the increase in available computing power, notably thanks to the parallel processing implemented in GPU cards. However, the transition from images to videos, then to multiple cameras implies a further change of scale in the amount of data processed. It also raises an issue that is often not addressed when it comes to image categorization. Indeed, in autonomous driving, an important task is to react as quickly as possible to a possible collision, for example when a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait for the pipeline to provide the correct response. This online processing is also a feature of processing in biological systems and could be an important first contribution if we could translate these principles into future automated processes. 
Second, a major constraint for future systems is energy cost. As we have seen, fast computation time has been maintained for high-dimensional images, but at the cost of higher energy consumption. In addition, the need to solve increasingly complex tasks has required the construction of increasingly complex and deep architectures. As an example, the best performing model in the Imagenet challenge uses billions of parameters that typically cost 1Wh to train and about 1Wh to infer a single image. Less power-hungry solutions have emerged, such as Mobile Net, but they are not yet ready for practical use in autonomous cars, as the additional power consumption would be about 300W, or 20\% of the energy of an electric car under standard conditions.

>>>>

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
Machine learning, and computer vision in particular, have undergone a major transformation in modern times, transitioning from an active actor in science fiction movies to become mainstream tools found in the smartphones in everyone's pocket. Less visible, but even more crucial to our economy and security, these automated tools now dominate the range of services that equip virtually most sectors of our daily lives. This trend is profoundly pronounced in the field of medicine, as it provides practitioners with new diagnostic tools to treat people faster and more effectively. This particular example also illustrates some important challenges that these tools are increasingly facing. One of these is their sensitivity to adversarial attacks, that is, the sensitivity of the models' output to minute changes in the input. This could raise important questions about the reliability of the results of any automated diagnostic model. More generally, these models do not explain why they produce a given output for a class of inputs. This lack of explainability is a hindrance to the advancement of these methodologies as well as to their acceptance for most safety-relevant tasks. Having said that, we may remember that these tools are inherited from theoretical models originally designed to understand the brain. While the first artificial neural networks were mainly applied to toy-like problems, they also offered a growing number of applications in machine learning and computer vision, but also more generally for task automation. In particular, convolutional neural networks are inspired by the feed-forward processing observed in the visual pathways of primates, and today they reach higher performances than humans for key image categorization challenges. One of the challenges of these models is to be able to scale them up for future applications, for example in autonomous driving. Indeed, in such applications, the input does not consist of a single image (say a few million pixels) but of a continuous stream of images from several cameras.

The challenges are numerous in such situations and two major obstacles must be highlighted: the computational delay and the energy budget. First, most existing solutions are built incrementally from models built to process low definition images, such as Le Net for MNIST~\citep{lecun1998gradient}, then high definition images, such as VGG on Imagenet~\citep{Simonyan:2014cmh}. This has a cost and notably the fact that the computation time increases with the size of the image. This phenomenon has been mitigated by the increase in available computing power, notably thanks to the parallel processing implemented in GPU cards. However, the transition from images to videos, then to multiple cameras implies a further change of scale in the amount of data processed. It also raises an issue that is often not addressed when it comes to image categorization. Indeed, in autonomous driving, an important task is to react as quickly as possible to a possible collision, for example when a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait for the pipeline to provide the correct response. This online processing is also a feature of processing in biological systems and could be an important first contribution if we could translate these principles into future automated processes. 
Second, a major constraint for future systems is energy cost. As we have seen, fast computation time has been maintained for high-dimensional images, but at the cost of higher energy consumption. In addition, the need to solve increasingly complex tasks has required the construction of increasingly complex and deep architectures. As an example, the best performing model in the Imagenet challenge uses billions of parameters that typically cost 1Wh to train and about 1Wh to infer a single image. Less power-hungry solutions have emerged, such as Mobile Net, but they are not yet ready for practical use in autonomous cars, as the additional power consumption would be about 300W, or 20\% of the energy of an electric car under standard conditions.
